---
title: "p8105_hw1_to2345"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load library:
```{r}
library(tidyverse)
```


## Problem 1: 
**Create a data frame comprised of:**

*   a random sample of size 8 from a standard Normal distribution
*   a logical vector indicating whether elements of the sample are greater than 0
*   a character vector of length 8
*   a factor vector of length 8, with 3 different factor “levels”
```{r question_1}
set.seed(1)
dataframe_1 = tibble(
  random_sample = rnorm(8, sd = 1),
  vec_logic = random_sample > 0,
  vec_char = character(8),
  vec_factor = factor(c(1,2,2,3,1,2,3,3))
)

```



**Take the mean of each variables:**

1.   The mean of the variable random_sample is `r round(mean(pull(dataframe_1, random_sample)), digits = 3)`.
2.   The mean of the variable vec_logic is `r round(mean(pull(dataframe_1, vec_logic)), digits = 3)`.
3.   The mean of the variable vec_char is `r round(mean(pull(dataframe_1, vec_char)), digits = 3)`.
4.   The mean of the variable vec_factor is `r round(mean(pull(dataframe_1, vec_factor)), digits = 3)`.

_We can see that the means of the created randome sample and the logic vector works. Yet, the means of the character vector and the factor vector does not work._



**Convert the logical vector to other data types, and multiply the random sample**

*   convert the logical vector to numeric, and multiply the random sample by the result
*   convert the logical vector to a factor, and multiply the random sample by the result
*   convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```{r}
log_to_num = as.numeric(pull(dataframe_1, vec_logic))
log_to_factor = as.factor(pull(dataframe_1, vec_logic))
factor_to_num = as.numeric(as.factor(pull(dataframe_1, vec_logic)))
```

1.   The result of multiply the random sample by the new numeric vector is `r round(log_to_num*pull(dataframe_1, random_sample), digit = 3)`.
2.   The result of multiply the random sample by the new factor  is `r round(log_to_factor*pull(dataframe_1, random_sample), digit = 3)`.
2.   The result of multiply the random sample by the new numeric vector which is converted from a factor is `r round(factor_to_num*pull(dataframe_1, random_sample), digit = 3)`.



## Problem 2: 
**Create a data frame comprised of:**
x: a random sample of size 500 from a standard Normal distribution
y: a random sample of size 500 from a standard Normal distribution
A logical vector indicating whether x + y > 1
A numeric vector created by coercing the above logical vector
A factor vector created by coercing the above logical vector

**create a new dataframe:**

```{r new_dataframe}
dataframe_2 = tibble(
  x = rnorm(500, mean = 0, sd = 1),
  y = rnorm(500, mean = 0, sd = 1),
  vec_logic = (x+y) > 1,
  vec_num = as.numeric(vec_logic),
  vec_factor = as.factor(vec_logic)
)
```

**Some description for this dataset**:

    1. The size of the dataset is `r nrow(dataframe_2)` by `r ncol(dataframe_2)`
    2. The mean, median, and standard deviation of x is `r round(mean(pull(dataframe_2, x)), digits = 3)`, `r round(median(pull(dataframe_2, x)), digits = 3)`, and `r round(sd(pull(dataframe_2, x)), digits = 3)` respectively.
    3. The proportion of cases for which x + y > 1 is `r 100*sum(with(dataframe_2, x+y > 1))/nrow(dataframe_2)`%


**Make a scatterplot of y vs x, color points using the logical variable**

```{r scatterplot_log}
plot_1 = ggplot(dataframe_2, aes(x = x, y = y, color = vec_logic)) + geom_point()
```

**Export this scatterplot using ggsave**
```{r}
ggsave("plot_hw1.png", plot = plot_1)
```



**Make a scatterplot of y vs x, color points using the numeric variable**

```{r scatterplot_num}
ggplot(dataframe_2, aes(x = x, y = y, color = vec_num)) + geom_point()
```


**Make a scatterplot of y vs x, color points using the factor variable**

```{r scatterplot_factor}
ggplot(dataframe_2, aes(x = x, y = y, color = vec_factor)) + geom_point()
```


